Lay Perceptions of Crowd-Scientific Findings: The Risks of Variability and Lack of Consensus

### 2021-10-08 talk/index.Rmd
Added results to talk

---
class: inverse, center, middle
name: discussion

>>>>

---
class: inverse, center, middle

# Main results

---
background-image: url("images/Figure1.jpg")
background-position: 50% 50%
background-size: 78%

Our main findings are displayed in Figure 1. Controlling for prior beliefs and comparing to the single-analyst condition, we found that (1) reported posterior beliefs were significantly lower in both the multi-consistent condition, b=-5.71, and the multi-inconsistent condition, b=-22.80; (2) ratings of credibility were significantly lower in the multi-inconsistent condition, b=-6.54, while they were not significantly different in the multi-consistent condition, b=1.24 (3) confidence in the effect size estimate was significantly lower in the multi-inconsistent condition, b=-9.09, while it was not significantly different in the multi-consistent condition, b=0.49; (4) ratings of bias were significantly greater in the multi-inconsistent condition, b=6.68, while they were not significantly different in the multi-consistent condition, b=2.13; and (5) ratings of error were significantly greater in both the multi-consistent condition, b=3.59, and the multi-inconsistent condition, b=5.89. For our exploratory measure of discretion, we found that ratings of experimenter degrees of freedom were significantly greater in both the multi-consistent condition, b=5.14, and the multi-inconsistent condition, b=9.22.

# Results: Multi-inconsistent

**In line with our hypotheses**, lay consumers of multi-analyst studies with **inconsistent** results  
--

`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
--

`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Find the results less credible  
--

`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have less confidence in the average effect size estimate  
--

`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from bias  
--

`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error  
--

$~~$  
For the additional **exploratory measure**, lay consumers of multi-analyst studies with **inconsistent** results
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom

In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias). 
---
.center[

# Results: Multi-consistent

**Contrary to our hypotheses**, lay consumers of multi-analyst studies with **consistent** results  
--

`r icon_style(icons::fontawesome("arrow-circle-down"), scale = 1.5, fill = "red")` $~~~$ Have lower posterior beliefs  
--

`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from error  
--

$~~$  
We found **no significant effects** on  
--

`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Credibility of the results  
--

`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Confidence in the effect size estimate  
--

`r icon_style(icons::fontawesome("question-circle"), scale = 1.5, fill = "grey")` $~~~$ Ratings of bias  
--

$~~$  
For the additional **exploratory measure**, lay consumers of multi-analyst studies with **consistent** results
`r icon_style(icons::fontawesome("arrow-circle-up"), scale = 1.5, fill = "green")` $~~~$ Believe the results are more likely to stem from experimenter degrees of freedom

In line with our hypotheses, lay consumers of multi-analyst studies with inconsistent results (compared to single-analyst studies) have lower posterior beliefs, find the results less credible, have less confidence in the average effect size estimate, and believe the results are more likely to stem from bias and error. Contrary to our hypotheses, we do not find that lay consumers of multi-analyst studies with consistent results (compared to single-analyst studies) have higher posterior beliefs, find the results more credible, have less confidence in the average effect size estimate, and believe the results are less likely to stem from bias and error: instead, they report significantly lower posterior beliefs and are more likely to believe the results stem from error (we did not find significant effects on ratings of credibility, confidence, or bias).

class: inverse, center, middle
name: discussion
